\section{General Information}

This document is intended as a template and guideline and should support the author in the course of doing the bachelor's thesis.
Assessment criteria comprise the quality of the theoretical and/or practical work as well as structure, content and wording of the written bachelor's thesis. Careful attention should be given to the basics of scientific work (e.g., correct citation).

\section{Structure of the Thesis}

The table of contents is followed by the introduction and the main part, which can vary according to the content. The bachelor's thesis ends with the bibliography (compulsory) and the appendix (optional).

\begin{itemize}
  \item	Cover page
  \item Acknowledgements
  \item Abstract of the thesis in English and German
  \item Table of contents
  \item Introduction (5-10\%)
  	\begin{itemize}
  		\item motivation
  		\item problem statement (which problem should be solved?)
  		\item aim of the work
  		\item methodological approach
  		\item structure of the work
  	\end{itemize}
  \item State of the art / analysis of existing approaches (10-30\%)
  	\begin{itemize}
  		\item literature studies
  		\item analysis
  		\item comparison and summary of existing approaches
  	\end{itemize}
  \item Suggested solution/Implementation/Methodology (20-50\%)
  	\begin{itemize}
  		\item used concepts
  		\item methods and/or models
  		\item languages
  		\item design methods
  		\item data models
  		\item analysis methods
  		\item formalisms
  	\end{itemize}
  \item Critical reflection (10-20\%)
  	\begin{itemize}
  		\item comparison with related work
  		\item discussion of open issues
  	\end{itemize}
  \item Summary and future work (5\%)
  \item Appendix: source code, data models, \dots
  \item Bibliography
\end{itemize}


\section{Recommendations}

\begin{itemize}
	\item Use primary literature, i.e., cite the original work.
	\item Refer diverse source of literature.
	\item Use active language (e.g., 'The programmer prepared a test plan and distributed it to the team' instead of 'A test plan was prepared and distributed to the team by the programmer'). 
	\item Cite all figures and tables in the text (e.g., Fig. 1 shows ...).
	\item Cite figures in the caption.
	\item Redraw cited figures.
	\item Use a spell checker (TexnicCenter => Extras => Options).
	\item Proof read the thesis several times. Let other people proof read your work.
	
	
\end{itemize}



 

